A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-01 dl-paper.tex
Fix 13, 14 of 3.5

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}
\usepackage{MnSymbol}

@@

\begin{document}
\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups. This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue for the functor $\K_2$ of a 1982 result of A.~Suslin and V.~Kopeiko. \end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. Thшы problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$:
\begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab). \end{equation} 
Dennis--Stein symbol $\langle a, b \rangle_\alpha$ can be expressed through Steinberg symbols in the special case when either $a$ or $b$ is an invertible element of $R$. More specifically, the following formulae hold (cf.~\cite[p.~250]{DS73}).
\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
 \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced. If $\Phi$ happens to be {\it nonsymplectic}, i.\,e. $\Phi \neq \rA_1, \rB_2, \rC_{\geq 3}$, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e. they satisfy the following identities: \begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}. \end{equation}
For these and other properties of symbols we refer the reader to~\cite{DS73}.

@@

Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
The only exception to this is~\cref{P0-conj-invariant} where the above subgroups are also used for $M=A$.
\begin{rem} \label{rem:recognition}
  From the above definition it follows that an element $z_\gamma(f, \xi)$ is a generator of type 1 provided $X \divides f$, $\gamma\neq\pm\alpha$ and $\gamma$ is not orthogonal to $\alpha$.
  Since $x_\gamma(f) = z_\gamma(f, 0)$, it follows that under the same assumptions $x_{\gamma}(f)$ is also a generator of type 1.
  In particular, if $\beta, \alpha - \beta \in \Phi$ then $x_{\pm(\alpha-\beta)}(Xf)$ is a generator of type 1.

  Similarly, if $\gamma - \alpha \in \Phi$ and $X \divides \xi$ then $z_\gamma(f, \xi)$ is a generator of type 2.
  In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\alpha+\beta}(f)$ is a generator of type 2.
\end{rem}

@@

Finally, let $g = x_\alpha(f)$ be a generator of type $5$. Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, $\epsilon = N_{\alpha, \beta}$ and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
\begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}

@@

For the rest of this section $M$ denotes the maximal ideal of $A$.
\begin{df} 
We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious homomorphism.
For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.

From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) \cdot g_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot g_2 \cdot x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \{X, (1+am)(1 + \tfrac{am'}{1+am})\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} 
Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for the generators of type 3 and 5.

Let $\beta$ be such that $\alpha + \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type $1$.
By~\cref{Zrels}\eqref{Z2}
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
and the latter expression a product of generators of type 5, 2, 1 (see~\cref{rem:recognition}).

Let $\beta$ be such that $\alpha - \beta \in \Phi$ and let $g = z_{\beta}(Xf, \xi)$ be a generator of type $1$. From~\cref{Zrels}~\eqref{Z3} we obtain that
\begin{equation} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
and the expression in the right-hand side is a product of generators of type 5, 2, 1.
Now let $g = z_{\beta}(f, X\xi)$ be a generator of type 2 (for $\beta$ as above). Again by~\cref{Zrels}~\ref{Z3}
\begin{equation} z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
\end{equation}
and the expression in the right-hand side are products of generators of type 5, 1, 2.

Let us verify the assertion for a generator of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} we obtain that
\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}

\begin{lemma} \label{lem:Tulenbaev-formula} 
One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation using~\eqref{eq:conj-h-x}--\eqref{eq:dennis-stein},\eqref{eq:symbol-properties} shows that
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}, \end{multline*}
which implies the assertion. \end{proof}

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Now by~\cref{lem:Smult} and~\cref{P0_conj} one has
\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}

The second assertion can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}

>>>>

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}

@@

\begin{document}
\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for even-dimensional orthogonal Steinberg groups. This result transfers to the orthogonal case an earlier result of M.~Tulenbaev and is also an analogue for the functor $\K_2$ of a 1982 result of A.~Suslin and V.~Kopeiko. \end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

Recall that Steinberg symbols are defined for arbitrary $s, t \in R^\times$ as follows:
\begin{equation} \label{eq:steinberg} \{ s, t \}_\alpha = h_\alpha(st) \cdot h_\alpha^{-1}(s) \cdot h_\alpha^{-1}(t). \end{equation}
In turn, Dennis--Stein symbols are defined for arbitrary $a, b\in R$ satisfying $1 + ab \in R^\times$:
\begin{equation} \label{eq:dennis-stein}  \langle a,b \rangle _ \alpha = x_{-\alpha}\left(\tfrac{- b}{1 + ab}\right) \cdot x_{\alpha}(a) \cdot x_{-\alpha}(b) \cdot x_{\alpha}\left(\tfrac{- a}{1+ab}\right) \cdot h_{\alpha}^{-1}(1 + ab). \end{equation} 
Dennis--Stein symbol $\langle a, b \rangle_\alpha$ can be expressed through Steinberg symbols in the special case when either $a$ or $b$ is an invertible element of $R$. More specifically, the following formulae hold (cf.~\cite[p.~250]{DS73}).
\begin{equation} \label{DS-S-relationship} \langle a, b \rangle_\alpha = \{-a, 1+ab\}_\alpha\text{ for } a, 1+ab\in R^\times,\ \
 \{ s, t \}_\alpha = \left\langle -s, \tfrac{1 - t}{s} \right\rangle_\alpha\text{ for } s, t\in R^\times. \end{equation}
Steinberg and Dennis--Stein symbols depend only on the length of $\alpha$, in particular they do not depend on $\alpha$ if $\Phi$ is simply-laced. If $\Phi$ happens to be {\it nonsymplectic}, i.\,e. $\Phi \neq \rA_1, \rB_2, \rC_{\geq 3}$, Steinberg symbols are antisymmetric and bimultiplicative, i.\,e. they satisfy the following identities: \begin{equation} \label{eq:symbol-properties} \{ u, st \} = \{ u, s\} \{ u, t \}, \ \{ u, v \} = \{ v, u\}^{-1}. \end{equation}
For these and other properties of symbols we refer the reader to~\cite{DS73}.
From~\eqref{eq:symbol-properties} it follows that
\begin{equation} \label{eq:symbol-inverse} \{u, v\}^{-1} = \{u^{-1}, v\} = \{u, v^{-1}\}. \end{equation}

@@

Almost always we will be using the above definition in the situation when $M$ is precisely the maximal ideal of $A$.
The only exception to this is~\cref{P0-conj-invariant} where the above subgroups are also used for $M=A$.
\begin{rem} \label{rem:recognition}
  From the above definition it follows that an element $z_\gamma(Xf, \xi)$ is a generator of type 1 provided $\gamma\neq\pm\alpha$ and $\gamma \not \perp \alpha$. Since $x_\gamma(Xf) = z_\gamma(Xf, 0)$, it follows that $x_{\gamma}(Xf)$ is also a generator of type 1. In particular, if $\beta, \alpha + \beta \in \Phi$ then $x_{\pm(\alpha+\beta)}(Xf)$ is a generator of type 1 and $x_{\alpha+\beta}(f)$ is a generator of type 2.
\end{rem}

@@

Finally, let $g = x_\alpha(f)$ be a generator of type $5$. Substituting in~\eqref{Z5} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$, and expressing the fifth factor in the right-hand side of~\eqref{Z5} through other terms we obtain that
\begin{multline} \label{eq:zalpha} g^{x_{-\alpha}(mX)} = z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
where $\epsilon = N_{\alpha, \beta}$. It is clear that the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4. \end{proof}

@@

For the rest of this section $M$ denotes the maximal ideal of $A$.
\begin{df}\label{S-def}
We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious homomorphism.
For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.

From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\begin{equation}\label{eq:S-def} S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\end{equation} \end{df}

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and the centrality of Steinberg symbols:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} 
Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for the generators of type 3 and 5.

Let $\beta$ be such that $\alpha + \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type $1$.
By~\cref{Zrels}\eqref{Z2}
\begin{equation}\label{eq:Zconj1} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi), \end{equation}
and the latter expression a product of generators of type 5, 2, 1 (see~\cref{rem:recognition}).

Let $\beta$ be such that $\alpha - \beta \in \Phi$ and $g = z_\beta(Xf, \xi)$ be a generator of type 1. By~\cref{Zrels}\eqref{Z3}
\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot af\xi^2) \cdot z_{\beta}(Xf, \xi), \label{eq:Zconj2} \end{equation}
and the expression in the right-hand side is a product of generators of type 5, 2, 1.

Now if $g = z_{\beta}(f, X\xi)$ is a generator of type 2 for $\alpha - \beta \in \Phi$, we obtain by~\cref{Zrels}\eqref{Z3} that
\begin{equation} g^{x_{\alpha}(aX^{-1})} = z_{\beta}(f, X\xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (af\xi) \cdot x_{\alpha-\beta} (N_{\beta,-\alpha}\cdot aXf\xi^2) \cdot z_{\beta}(f, X\xi).
\end{equation} and the expression in the right-hand side is a product of generators of type 5, 1, 2.

It remains to verify the assertion for a generator $g = x_{-\alpha}(X^2f)$ of type 4.
Choose $\beta\in \Phi$ such that $\alpha+\beta \in \Phi$. 
Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = -\alpha - \beta$ into~\eqref{Z5} we obtain that
\begin{multline} \label{eq:Zconj3} z_{-\alpha}(X^2f, aX^{-1}) = x_{-\alpha-\beta}(\epsilon Xf) \cdot x_{-\beta}(-af) \cdot x_{\beta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{-\alpha-\beta}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha+\beta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{-\beta}(a f, -X), \end{multline}
where $\epsilon = N_{-\alpha-\beta,\beta}$. 
Clearly, the expression in the right-hand side is a product of generators of type 1, 2, 1, 4, 1, 1, 5, 2. \end{proof}

\begin{lemma} \label{lem:Tulenbaev-formula} 
One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
 \begin{align} 
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) &\text{ by~\eqref{eq:conj-h-x}} \label{eq:Tf-comp} \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) &\text{ by~\eqref{eq:dennis-stein}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) &\text{ by~\eqref{eq:conj-h-x}, \eqref{eq:conj-h-h}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right)&\text{ by~\eqref{eq:steinberg}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}. \nonumber \end{align}
The assertion of the lemma now follows from the following computation:
\begin{align*}
 S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}  \end{proof}

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Direct computation shows that
\begin{align*}
 S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)&\text{ by~\cref{lem:Smult}} \\\
 = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle &\text{ by~\cref{lem:Tulenbaev-formula}.}
\end{align*}
By \cref{P0_conj} and \cref{rem:c-DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$. Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$.

The second assertion of the lemma can be verified directly using~\eqref{eq:symbol-properties}. \end{proof}
